---
title: "R Notebook"
output: html_notebook
---
 More trees on the web: Open Tree of Life, Tree Base, ROTL (1 point)

You should explore Open Tree of Life and TreeBase at their webpages.

You may need to register and make an account. (Save your usernames and passwords!)

Work through the R Notebook 3.2, which uses an R Package called ROTL to interact with the Interactive Tree of Life (iTOL) - see how ROTL can access its resources

```{r}
library("rotl")
ß
tnrs_contexts()
```


```{r}
taxa <- c("Alnus", "Pyrus", "Fraxinus", "Tilia", "Betula", "Aesculus", "Rhamnus", "Catalpa", "Prunus", "Castanea", "Populus", "Cupressus", "Cornus", "Pseudotsuga", "Corylus", "Sequoiadendron", "Crataegus", "Tsuga", "Gleditsia", "Ilex", "Calocedrus", "Juniperus", "Larix", "Arbutus", "Acer", "Sorbus", "Cercocarpus", "Quercus", "Pinus", "Thuja", "Sequoia", "Elaeagnus", "Picea", "Liquidambar", "Platanus", "Lithocarpus", "Cedrus", "Abies", "Juglans", "Chamaecyparis", "Liriodendron", "Taxus")

resolved_names <- tnrs_match_names(taxa, context_name = "Vascular plants")
resolved_names
in_tree <- is_in_tree(ott_id(resolved_names))
in_tree
my_tree <- tol_induced_subtree(ott_ids = resolved_names$ott_id)
plot(my_tree, no.margin=TRUE)
plot(my_tree, type="fan")
```

```{r}
fagus_id <- tnrs_match_names("fagus")
fagus_id
fagus_tree <- tol_subtree(ott_id = ott_id(fagus_id))
plot(fagus_tree, type = "fan")
```

## SAVING DISPLAYED TREES

```{r}
pdffn = "fagus_id.pdf"
pdf(file=pdffn)
plot(fagus_id, type="unrooted", edge.width=5, edge.color="blue", lab4ut="axial")
dev.off()
```
